Exposing Disputed Statements on the Web

### 2009-03-22 papers/uist_thinklink/thinklink.tex
More paper work + associated bug fixes

\keywords{CSCW, sensemaking, web, browsers, collaboration, mind mapping}

@@

\keywords{Sense-making, Annotation, Argumentation, Web}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_popup.png}
	\caption{Click on a claim to investigate evidence for and against it}
	\label{claimview}
	\end{center}
\end{figure}

@@

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
	\caption{Hovering over a highlighted snippet shows a summary}
	\label{highlight}
	\end{center}
\end{figure}

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
	\caption{Use topic suggestion to quickly file evidence snippets}
	\label{sniptopic}
	\end{center}
\end{figure}

\subsection{Organizing the Argument Graph}

\todo{Talk about organizing stuff}

\subsection{Creating new Snippets}
\label{newsnippet}

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
	\caption{Process for creating a new snippet}
	\label{createprocess}
	\end{center}
\end{figure*}

%\begin{figure}[tb]
%	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
%	\caption{The claim selection window allows one to identify the claim a snippet is making}
%	\label{snipsavefull}
%\end{figure}

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
	\caption{Selecting the claim made by a new snippet}
	\label{snipsavecrop}
\end{figure}

There are several reasons a user may wish to add a snippet to Think Link. They may find the snippet useful and may want to refer to it again in the future; they may disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments; they may think the claim argues a point well and want to be able to use it to make an argument, or they may agree with the claim and want to provide easy access to evidence elsewhere that backs it up.

To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser tool bar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}). This is a similar approach to that taken clipping tools such as Google Notebook.

Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making. To do this, Think Link presents the user with a ``claim selector'' window. This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making.

Since much of Think Link's utility comes from linking snippets together, it is important to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. We designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim. This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected. In practice, it is inevitable that duplicates claims and topics will sometimes be created. When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.

@@

\todo{Describe how one goes about marking disputed claims}.

If a user has added the Think Link extension to their browser then it will highlight snippets that make disputed claims (Figure~\ref{highlight}). If

an open database of contentious claims, and an interactive claim browser that allows one to explore the various snippe

If a user has added the Think Link extension to their browser then it will highlight

Think Link is a browser plugin that is designed to help users tell when the information that they read on the web is inaccurate or presents only one side of a contentious issue. As the user browses the web, Think Link

% 
% 
% \subsection{The Mental Model}
% 
% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
% 	\caption{Icons used for Claims, Snippets, and Topics}
% 	\label{bookmark_icons}
% 	\end{center}
% \end{figure}
% 
% Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}): 	
% 
% \begin{itemize}
% \item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming is man made''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
% \item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
% \item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can be about one or more topics, and a topic can have one or more more general topics. Topics are used to organize and disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous. A topic can itself by disambiguated by having a super-topic.
% \end{itemize}
% 
% 
% \subsection{Browsing factual claims}
% \label{browseclaim}\label{claimbrowser}
% 
% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
% 	\caption{The claim browser visualizes the claim graph}
% 	\label{claimbrowse_diagram}
% 	\end{center}
% \end{figure}
% 
% 
% Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
% A topic can have any number of more specific topics (e.g. ``US Election 2008'' is more specific than ``US Elections'') and any number of more general topics. A topic can also have any number of claims about that topic.
% 
% When designing an interface to this structure, we were faced with two opposing constraints. We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree. Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place. Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
% 
% After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner. Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it. Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.
% 
% The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards. A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
% 
% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
% 	\caption{Close up of a list of supporting claims}
% 	\label{claimbrowse_zoom}
% 	\end{center}
% \end{figure}
% 
% Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states. When a new item is selected, it grows in size and moves to the center. Other items that were already on the screen move from their current locations to their new locations. Other objects appear and disappear by smoothly sliding into or out of view. 
% 
% Users see a claim browser in three different places. The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}). The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}). The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).

\subsection{Organizing the Claim Graph}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
	\caption{The Claim Organizer contains two claim browsers}
	\label{fig:claimbrowser}
	\end{center}
\end{figure}

Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph. The claim graph is shared between all users and editable by anyone. Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects. One can think of Think Link as being rather like a wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.

Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim. If a user finds a snippet or claim interesting then they can vote in favor of it by clicking on its icon, causing it to light up (Figure~\ref{bookmark_icons}). When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them as interesting.

It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with. Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets. While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering. If a user believes a claim, topic, snippet, or connection is junk then they can request that it be deleted by clicking on the ``delete'' button. This will hide the object for the user who request deletion and reduce the score of the object for other users. If enough people vote to delete the object then its score will eventually be low enough that it is not displayed to users unless they request to see junk objects.

In a wiki, users edit and delete information produced by others, and history is used to revert abusive changes. Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects. The hope is that over time ratings should converge to a steady state and edit wars should be avoided. It would not be practical for a wiki to take this approach as wiki data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.

Think Link uses the familiar drag and drop interface for establishing new connections. To establish a connection between two claims, one need simply drag one claim onto the other. The claim organizer window has two claim browsers, allowing a user to points from one browser onto points on the other (Figure~\ref{fig:claimbrowser}).

\subsection{Why People Annotate}

Tools like Think Link rely on user contributions in order to be useful. If no users are identifying factual claims on pages then other people who browse such pages will not see any claims identified. Similarly, if no other users are connecting claims together, then users will not see any supporting or opposing claims when they click on a highlighted snippet.

Moreover, in order to become popular, a tool like Think Link needs to be useful even when very few people are using it. If a tool is only useful when it has a large community using it then it is unlikely that early adopters will stick with it enough for it to ever acquire a large community.

Our user study participants identified several reasons why they would want to mark up factual claims in documents they found. The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found. One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments. The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.

Think Link is implemented as three largely independent components:

\begin{itemize}
\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
\item {\bf A web UI}, written using Javascript that implements the claim browser
\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page. This script displays the web UI in an iframe to pick or investigate a claim.
\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides tool bar and context-menu shortcuts.
\end{itemize}

These components are largely independent. One could use the page enhancement script on a web page without using the Firefox extension, by either manually including it on the page (e.g. to enhance your own blog) or by adding it using a proxy. Since the server API is public, one could write alternative tools that mark up web pages in different ways, or use the claim graph for different purposes.

The source code to Think Link is publicly available under the Apache license.

>>>>

@@

\keywords{CSCW, Sensemaking, Annotation, Argumentation, Web}

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
	\caption{Think Link highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
	\caption{Click on a claim to investigate evidence for and against it}
	\label{claimview}
	\end{center}
\end{figure}

\todo{Claim panel should have 'more' buttons}

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
	\caption{A claim panel presents information for and against a claim}
	\label{panel}
	\end{center}
\end{figure}

@@

If a user has installed the Think Link browser extension then they can create a snippet from text on a web page by selecting the text and selecting either ``This is disputed'' or ``This is interesting'' from the context menu. A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful information that would be useful to readers investigating a disputed claim.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_snipmark.png}
	\caption{Use the context menu to mark a new snippet}
	\label{createprocess}
	\end{center}
\end{figure}

Think Link does not require that a user associate a snippet with a snippet at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. One anticipated usage scenario for Think Link is an activist user who users a search engine to find a large number of snippets that make a clam that the user disagrees with. In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.

Think Link provides three ways for a user to associate a claim with a snippet:

\begin{description}
\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}). A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates to'' link types. If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_sugsnippet.png}
	\caption{Claim first: Pick unfiled snippets to attach to a claim}
	\label{snipclaim}
	\end{center}
\end{figure}

\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a snippet (Figure~\ref{sniptopic}). If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet. As with the snippet suggested, a user can guide the suggestions by entering keywords. If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
	\caption{Snippet first: Pick a claim or topic for each unfiled snippet}
	\label{sniptopic}
	\end{center}
\end{figure}

\item[Immediate:] A user can select a claim for a snippet that they have just marked. When a user marks a snippet, Think Link will initially highlight it in blue to show the user that the snippet is not currently associated with a claim or topic and will not be shown to other users. If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
\end{description}

When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim. It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to offer support for a particular claim. In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for. In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.

Think Link uses the Wikify! algorithm~\cite{Mihalcea} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.

\todo{Mention about topic previewing}

As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected. If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together.

\todo{Allow two claims to be marked as being identical}.

Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.

\todo{BUG: don't have 'add' button for snippets}

@@

\todo{finish this section}
